Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-22 conclusions.tex
fixed broken citation
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@756 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have demonstrated a computationally feasible procedure for the rapid
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar mass black holes.  These sources are expected to produce
prompt electromagnetic signals and may be the progenitors of some short-hard
gamma ray bursts.  Rapid alerts to the broader astronomical community may
improve the chances of detecting an electromagnetic counterpart in bands from
X-ray down to radio.  We antipate requiring no more than \numcpus\ modern
computer cores to analyze a four detector network of gravitational wave data
for such systems assuming spin effects can be ignored in parameterizing the
expected signals ~\cite{the papers that say that is okay}.  This is within the
current computing capabilities of the LSC data grid\cite{LDG}.

>>>>

We have demonstrated a computationally feasible procedure for the rapid
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar mass black holes.  These sources are expected to produce
prompt electromagnetic signals and may be the progenitors of some short-hard
gamma ray bursts.  Rapid alerts to the broader astronomical community may
improve the chances of detecting an electromagnetic counterpart in bands from
X-ray down to radio.  We antipate requiring no more than \numcpus\ modern
computer cores to analyze a four detector network of gravitational wave data
for such systems assuming spin effects can be ignored in parameterizing the
expected signals ~\cite{the-papers-that-say-that-is-okay}.  This is within the
current computing capabilities of the LSC data grid\cite{LDG}.
